---
title: "Homework7"
author: "HudsonPlaskoff"
date: "2026-03-06"
output:
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(ggthemes)
library(knitr)
```

## Filter Diamonds Dataset^[Question 1 complete]

```{r}
diamonds_filtered <- diamonds %>%
  filter(
    color == "D" | color == "G" | color == "J",
    clarity == "I1" | clarity == "VS1" | clarity == "IF"
    )

diamonds_filtered_combinations <- diamonds_filtered %>%
  group_by(color,clarity) %>%
  summarize(n=n())

knitr::kable(diamonds_filtered_combinations)
```

## Visualization of Price and Carat

```{r}
ggplot(
  diamonds_filtered,
  aes(x=carat,y=price)
  ) +
  geom_point(alpha=0.5) +
  geom_smooth(method="lm")
```

There is a positive relationship between prices and carats for diamonds.^[Question 2 complete]

## Visualization of Price, Carat, and Color

```{r}
ggplot(
  diamonds_filtered,
  aes(x=carat,y=price)
  ) +
  geom_point(alpha=0.5,aes(color=color)) +
  geom_smooth(method="lm",aes(color=color))
```

## Visualization of Price, Carat, Color, and Clarity

```{r}

```

## Faceted Visualization of Price, Carat, Color, and Clarity

```{r}

```

## Price-Carat Ratios of Color-Clarity Combinations

```{r}

```