---
title: "Homework7"
author: "HudsonPlaskoff"
date: "2026-03-06"
output:
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
library(tidyverse)
library(ggplot2)
library(ggthemes)
library(knitr)
```

## Filter Diamonds Dataset^[Question 1 complete]

```{r}
diamonds_filtered <- diamonds %>%
  filter(
    color == "D" | color == "G" | color == "J",
    clarity == "I1" | clarity == "VS1" | clarity == "IF"
    )

diamonds_filtered_combinations <- diamonds_filtered %>%
  group_by(color,clarity) %>%
  summarize(n=n())

knitr::kable(diamonds_filtered_combinations)
```

## Visualization of Price and Carat

```{r}
ggplot(
  diamonds_filtered,
  aes(x=carat,y=price)
  ) +
  geom_point(alpha=0.5) +
  geom_smooth(method="lm")
```

There is a positive relationship between prices and carats for diamonds.^[Question 2 complete]

## Visualization of Price, Carat, and Color

```{r}
ggplot(
  diamonds_filtered,
  aes(x=carat,y=price)
  ) +
  geom_point(alpha=0.5,aes(color=color)) +
  geom_smooth(method="lm",aes(color=color))
```

There is a positive relationship between prices and carats for diamonds, regardless of color. However, this relationship is most positive for D (best color), slightly less positive for G (middle-grade color), and even less positive for J (worst color).^[Question 3 complete]

## Visualization of Price, Carat, Color, and Clarity

```{r}
ggplot(
  diamonds_filtered,
  aes(x=carat,y=price)
  ) +
  geom_point(alpha=0.5,aes(color=color,shape=clarity)) +
  geom_smooth(method="lm",aes(color=color))
```

This scatterplot is somewhat crowded, making it difficult to make any conclusive analysis of the data.^[Question 4 complete]

## Faceted Visualization of Price, Carat, Color, and Clarity

```{r}
ggplot(
  diamonds_filtered,
  aes(x=carat,y=price)
  ) +
  geom_point(alpha=0.5) +
  geom_smooth(method="lm") +
  facet_grid(color~clarity)
```

The steepest relationship is between IF (best clarity) and D (best color). As the color and clarity decrease respectively, the relationship becomes less positive, with the weakest (although still positive) relationship being between I1 (worst clarity) and J (worst color).^[Question 5 complete]

## Price-Carat Ratios of Color-Clarity Combinations

```{r}
diamonds_filtered <- diamonds_filtered %>%
  mutate(
    price_per_carat = price/carat
  ) %>%
  group_by(color,clarity) %>%
  summarize(price_per_carat = mean(price_per_carat)) %>%
  arrange(desc(price_per_carat))

knitr::kable(diamonds_filtered)
```

The data shown on this table agrees with the data shown from the earlier visualizations, especially the faceted scatterplots from Question 5. This reiterates that there is a positive relationship between price and carat. This also reiterates that this relationship is more positive if color and clarity are higher and less positive if color and clarity are lower.^[Question 6 complete]